\documentclass{ctexart}

\newcounter{evoc}
\newcommand{\simp}[1]{$*$\textsl{#1}}
\newcommand{\key}{}
\newcommand{\voc}[3]{\par \stepcounter{evoc} \renewcommand{\key}{\textbf{#1}} \noindent \subentrynote \, \textbf{#1}: #2. ---\textit{#3}}
\newcommand{\aaa}{\=a}
\newcommand{\ii}{\=i}
\newcommand{\oo}{\=o}
\newcommand{\ee}{\=e}
\newcommand{\ddd}{$\cdots$}
\newcommand{\ent}{\textsuperscript}
\newcommand{\subentrynote}{$\bullet$}

\newcommand{\ety}[2]{\\ \noindent \textsc{Latina} \quad #1 (\textsl{#2})}
\newcommand{\fety}[2]{\\ \noindent \textsc{Français} \quad #1 (\textsl{#2})}
\begin{document}

\section{盎格魯文}
\subsection{Vocabulary}
\subsubsection*{The Unexpected Scalia}
\newcommand{\sth}{\textsl{sth}}
\voc{at times}{occasionally}{..., \key\ vexingly so.}
\voc{vexingly}{extremely}{..., at times \key\ so.}
\ety{vexs\aaa ti\oo}{shaking}
\voc{on the merits}{based upon fact and law}{In fact, the number totals 135 out of 867 opinions \key.}
\voc{compel}{to force}{...that his legal philosophy \key led him to do so.}
\ety{compellere}{to compel}
\voc{ahistorical}{to lack historical context}{His conservative views on the Second Amendment seem \key, but then, ...}
\voc{doctrine}{a belief or principle}{... to subject the \key\ of originalism to serious scrutiny.}
\ety{doctrīna}{teaching, instruction}
\voc{scrutiny}{intense study of \sth}{... to subject the doctrine of originalism to serious \key.}
\ety{scrūtinium}{a search, an inquiry}
\voc{construe}{to interpret}{... the Constitution should be \key d the same way it was understood ...}
\ety{cōnstruere}{to pile together}
\voc{reactionary}{Favoring a return to the past}{While an amazing document for its time, the eighteenth-century Constitution would be a \key\ document today.}
\fety{réactionnaire}{a person opposing the revolution}
\voc{abomination}{a disgusting vice}{While those \key s have largely been eliminated ...}
\ety{abōminātiō}{abomination}
\voc{seditious}{related to rebellion}{... Congress could pass a law criminalizing \key\ libel and executing someone for forgery.}
\ety{sēditiō}{insurrection, rebellion}
\voc{libel}{a false statement to damage reputation}{... Congress could pass a law criminalizing seditious \key\ and executing someone for forgery.}
\ety{libellus}{petition}
\voc{forgery}{fraudulently making or altering a writing or signature}{...Congress could pass a law criminalizing seditious libel and executing someone for \key.}
\ety{fabricāre}{fabricate}
\voc{germane}{related to}{... information about the understanding of the Framers, ..., that are germane to present issues are so few ...}
\ety{germānus}{of brothers or sisters}
\voc{resort to}{the using of \sth\ because it is the only thing available}{... that many constitutional judgments cannot be determined by \key\ history.}
\voc{advocacy}{the act to arguing or advocating}{..., they undoubtedly have had a greater impact on his influence, including his status as role model and molder of Supreme Court \key.}
\ety{advocāre}{to call for}
\voc{laugh \sth\ out of court}{to reject an idea as absurd}{I join the opinion of the Court except that portion which which takes seriouly, ..., an argument that shoud be \textbf{laughed out of the court}.}
\voc{dismissive}{showing disregard}{Scalia was equally \key\ of some of Kennedy's opinions, ...}
\ety{dimissus}{to sent away, dismiss}
\voc{sweet-mystery-of-life passage}{\simp{雞湯判決書}}{..., ridiculing, for example, what he called Kennedy's ``\key'' in Lawrence v. Texas (2003) ...}
\voc{aphorism}{saying}{The SCOTUS has descended from the disciplined legal reasoning of John Marshall and Joseph Story to the mystical \key s of the fortune cookie.}
\ety{aphorismus}{aphorism}
\voc{fortune cookie}{\simp{籤語餅}}{The SCOTUS has descended from the disciplined legal reasoning of John Marshall and Joseph Story to the mystical aphorisms of the \key.}
\voc{perceived}{widely recognized to be true}{What seemed to bother Scalia most was the \key\ absence of  a coherent and rigorous philosophy on the part of Stevens, ...}
\ety{percipere}{observe, note}
\voc{coherent}{logically organized}{What seemed to bother Scalia most was the perceived absence of  a \key\ and rigorous philosophy on the part of Stevens, ...}
\ety{cohaerens}{uniting}
\subsubsection*{Judgements}
\voc{balance of possibilities}{burden of proof, more likely than not}{... the accused has a good defence if he can prove on the \key\ that ...}
\voc{be confined to}{be restricted to}{... the accused \textbf{is confined to} relying on the statutory defences expressly provided for ...}
\subsubsection*{Latin Phrases and Abbreviations}
\voc{ad hoc}{formed or done for a particular purpose only}{An \key\ committee was set up to oversee the matter.}
\voc{ad nauseam}{repeating or continuing to the point of boredom}{The apparent risks of secondary smoking have been debated \key.}
\voc{bona fide}{in good faith}{Although he failed, the prime minister made a \key\ attempt to repair the nation's damaged economy.}
\voc{c.}{circa, approximately}{The house was built \key\ 1870.}
\voc{compos mentis}{in control of the mind }{Please call me back later when I'm \key.}
\voc{de facto}{in fact}{Although the Emperor was the head of state, the \key\ ruler of Japan was the Shogun.}
\voc{ergo}{therefore}{Neither side would have an incentive to start a war. \key, peace  would reign.}
\voc{erratum}{error}{An \key\ is a correction of a published text.}
\voc{ex gratia}{from kindness or grace ,without recognizing any liability or legal obligation}{They received an undisclosed \key\ payment.}
\voc{in loco parentis}{in the place of a parent}{Teachers sometimes have to act \key.}
\voc{in situ}{in its original place}{The paintings have been taken to the museum but the statues have been left \key.}
\voc{inter alia}{among other things}{The report covers, \key, computers, telecommunications and air travel.}
\voc{n.b.}{nota bene, note well}{I have corrected the issue with the new flash update. \textbf{N.B.} if you manually install the update when prompted your software will break again.}
\voc{p.a.}{per annum, for each year}{The population is increasing by about 2\% \key.}
\voc{per se}{in itself/themselves; intrinsically}{These facts \key\ are not important.}
\voc{post-mortem}{autopsy}{The \key\ revealed that she had been murdered.}
\voc{pro rata}{proportional; proportionally}{The car rental charge is \$50 per day and then \key\ for part of a day.}
\voc{quid pro quo}{favour or advantage given or expected in return for something}{Is it simply a wild fantasy, or a mistake on the part of the old man — some impossible \key?}
\voc{verbatim}{in exactly the same words}{I had to memorize the text \key.}
\voc{persona non grata}{unacceptable or unwelcome person}{From now on, you may consider yourself \key\ in this house.}
\par
\vspace{2cm}
\arabic{evoc} new vocabularies in total.
\end{document}